\dppTitle

### 2014-02-28 manuscripts/dpp-msbayes/dpp-msbayes-abstract.tex
Breaking up dpp ms into more files.
Moving abstract and acknowledgments to separate files, and also making
the title a macro.

%&<latex>
\documentclass[letterpaper,12pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../utils/preamble.tex}
\input{../utils/macros.tex}

\title{An Improved Approximate-Bayesian Model-choice Method for Estimating
Shared Evolutionary History}

\author[1]{Jamie R.\ Oaks\thanks{Corresponding author: \href{mailto:joaks1@gmail.com}{\tt joaks1@gmail.com}}\thanks{Current address: Department of Biology, University of Washington, Seattle, Washington 98195}}
% \author[1]{Mark T.\ Holder}
\affil[1]{Department of Ecology and Evolutionary Biology, University of Kansas, Lawrence, Kansas 66045}

% \date{\today}
\date{\parbox{\linewidth}{\centering%
    \today\endgraf\bigskip
    \textbf{Running head}: Improved Estimation of Shared Evolutionary History}}

\makeatletter
\let\msTitle\@title
\let\msAuthor\@author
\let\msDate\@date
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% \doublespacing
% \raggedright
% \setlength{\parindent}{0.5in}
% \begin{linenumbers}

\maketitle

\begin{abstract}
    To understand the processes that generate biodiversity, it is
    important to account for large-scale processes that affect the evolutionary
    history of groups of co-distributed populations of organisms.
    Such events predict temporally clustered divergences times, a pattern
    that can be estimated using genetic data from co-distributed species.
    I introduce a new approximate-Bayesian method for comparative
    phylogeographical model-choice that estimates the temporal distribution of
    divergences across taxa from multi-locus DNA sequence data.
    The model is an extension of that implemented in \msb.
    By reparameterizing the model, introducing more flexible priors on
    demographic and divergence-time parameters, and implementing a
    non-parametric Dirichlet-process prior over divergence models, I improved
    the robustness, accuracy, and power of the method for estimating shared
    evolutionary history across taxa.
    The results demonstrate the improved performance of the new method is due
    to (1) more appropriate priors on divergence-time and demographic
    parameters that avoid prohibitively small marginal likelihoods for models
    with more divergence events,
    and (2) the Dirichlet-process providing a flexible prior on divergence
    histories that does not strongly disfavor models with intermediate numbers
    of divergence events.
    % The results demonstrate that the tendency of the \msb model to spuriously
    % support models of clustered divergences is caused by a combination of (1)
    % uniform priors on nuisance parameters hindering the marginal likelihoods of
    % models with more divergence-time parameters, and (2) a prior on divergence
    % models that disfavors models with intermediate numbers of divergence-time
    % parameters.
    The new method yields more robust estimates of posterior uncertainty, and
    thus greatly reduces the tendency of the model to incorrectly estimate
    biogeographically interesting models with strong support.

    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Dirichlet-process prior; approximate Bayesian
    computation; model choice; phylogeography; biogeography} 
\end{abstract}

\newpage

\input{dpp-msbayes-main.tex}

\section{Acknowledgments}
I am greatful to Melissa Callahan, Mark Holder, Emily McTavish, Daniel Money,
Jordan Koch, and Adam Leach\'{e} for insightful comments that greatly improved
this work.
I thank the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
This work was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
I also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.

\bibliography{../bib/references}

%% LIST OF FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\singlespacing

\renewcommand\listfigurename{Figure Captions}
\cftsetindents{fig}{0cm}{2.2cm}
\renewcommand\cftdotsep{\cftnodots}
\setlength\cftbeforefigskip{10pt}
\cftpagenumbersoff{fig}
\listoffigures

% \end{linenumbers}

%% TABLES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\singlespacing

\input{dpp-msbayes-tables.tex}

\clearpage

%% FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\input{dpp-msbayes-figures.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SUPPORTING INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}

\singlespacing

\section*{Supporting Information}
% PUT MAIN TEXT CITATION HERE
\hangindent=1cm
Oaks, J.\ R. \msTitle.

\newpage
\singlespacing

\input{dpp-msbayes-si-figures.tex}

\end{document}

>>>>

To understand the processes that generate biodiversity, it is
important to account for large-scale processes that affect the evolutionary
history of groups of co-distributed populations of organisms.
Such events predict temporally clustered divergences times, a pattern
that can be estimated using genetic data from co-distributed species.
I introduce a new approximate-Bayesian method for comparative
phylogeographical model-choice that estimates the temporal distribution of
divergences across taxa from multi-locus DNA sequence data.
The model is an extension of that implemented in \msb.
By reparameterizing the model, introducing more flexible priors on
demographic and divergence-time parameters, and implementing a
non-parametric Dirichlet-process prior over divergence models, I improved
the robustness, accuracy, and power of the method for estimating shared
evolutionary history across taxa.
The results demonstrate the improved performance of the new method is due
to (1) more appropriate priors on divergence-time and demographic
parameters that avoid prohibitively small marginal likelihoods for models
with more divergence events,
and (2) the Dirichlet-process providing a flexible prior on divergence
histories that does not strongly disfavor models with intermediate numbers
of divergence events.
% The results demonstrate that the tendency of the \msb model to spuriously
% support models of clustered divergences is caused by a combination of (1)
% uniform priors on nuisance parameters hindering the marginal likelihoods of
% models with more divergence-time parameters, and (2) a prior on divergence
% models that disfavors models with intermediate numbers of divergence-time
% parameters.
The new method yields more robust estimates of posterior uncertainty, and
thus greatly reduces the tendency of the model to incorrectly estimate
biogeographically interesting models with strong support.

### 2014-02-28 manuscripts/dpp-msbayes/dpp-msbayes-acknowledgments.tex
Breaking up dpp ms into more files.
Moving abstract and acknowledgments to separate files, and also making
the title a macro.

%&<latex>
\documentclass[letterpaper,12pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../utils/preamble.tex}
\input{../utils/macros.tex}

\title{An Improved Approximate-Bayesian Model-choice Method for Estimating
Shared Evolutionary History}

\author[1]{Jamie R.\ Oaks\thanks{Corresponding author: \href{mailto:joaks1@gmail.com}{\tt joaks1@gmail.com}}\thanks{Current address: Department of Biology, University of Washington, Seattle, Washington 98195}}
% \author[1]{Mark T.\ Holder}
\affil[1]{Department of Ecology and Evolutionary Biology, University of Kansas, Lawrence, Kansas 66045}

% \date{\today}
\date{\parbox{\linewidth}{\centering%
    \today\endgraf\bigskip
    \textbf{Running head}: Improved Estimation of Shared Evolutionary History}}

\makeatletter
\let\msTitle\@title
\let\msAuthor\@author
\let\msDate\@date
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% \doublespacing
% \raggedright
% \setlength{\parindent}{0.5in}
% \begin{linenumbers}

\maketitle

\begin{abstract}
    To understand the processes that generate biodiversity, it is
    important to account for large-scale processes that affect the evolutionary
    history of groups of co-distributed populations of organisms.
    Such events predict temporally clustered divergences times, a pattern
    that can be estimated using genetic data from co-distributed species.
    I introduce a new approximate-Bayesian method for comparative
    phylogeographical model-choice that estimates the temporal distribution of
    divergences across taxa from multi-locus DNA sequence data.
    The model is an extension of that implemented in \msb.
    By reparameterizing the model, introducing more flexible priors on
    demographic and divergence-time parameters, and implementing a
    non-parametric Dirichlet-process prior over divergence models, I improved
    the robustness, accuracy, and power of the method for estimating shared
    evolutionary history across taxa.
    The results demonstrate the improved performance of the new method is due
    to (1) more appropriate priors on divergence-time and demographic
    parameters that avoid prohibitively small marginal likelihoods for models
    with more divergence events,
    and (2) the Dirichlet-process providing a flexible prior on divergence
    histories that does not strongly disfavor models with intermediate numbers
    of divergence events.
    % The results demonstrate that the tendency of the \msb model to spuriously
    % support models of clustered divergences is caused by a combination of (1)
    % uniform priors on nuisance parameters hindering the marginal likelihoods of
    % models with more divergence-time parameters, and (2) a prior on divergence
    % models that disfavors models with intermediate numbers of divergence-time
    % parameters.
    The new method yields more robust estimates of posterior uncertainty, and
    thus greatly reduces the tendency of the model to incorrectly estimate
    biogeographically interesting models with strong support.

    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Dirichlet-process prior; approximate Bayesian
    computation; model choice; phylogeography; biogeography} 
\end{abstract}

\newpage

\input{dpp-msbayes-main.tex}

\section{Acknowledgments}
I am greatful to Melissa Callahan, Mark Holder, Emily McTavish, Daniel Money,
Jordan Koch, and Adam Leach\'{e} for insightful comments that greatly improved
this work.
I thank the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
This work was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
I also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.

\bibliography{../bib/references}

%% LIST OF FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\singlespacing

\renewcommand\listfigurename{Figure Captions}
\cftsetindents{fig}{0cm}{2.2cm}
\renewcommand\cftdotsep{\cftnodots}
\setlength\cftbeforefigskip{10pt}
\cftpagenumbersoff{fig}
\listoffigures

% \end{linenumbers}

%% TABLES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\singlespacing

\input{dpp-msbayes-tables.tex}

\clearpage

%% FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\input{dpp-msbayes-figures.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SUPPORTING INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}

\singlespacing

\section*{Supporting Information}
% PUT MAIN TEXT CITATION HERE
\hangindent=1cm
Oaks, J.\ R. \msTitle.

\newpage
\singlespacing

\input{dpp-msbayes-si-figures.tex}

\end{document}

>>>>

I am greatful to Melissa Callahan, Mark Holder, Emily McTavish, Daniel Money,
Jordan Koch, and Adam Leach\'{e} for insightful comments that greatly improved
this work.
I thank the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
This work was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
I also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.

### 2014-02-28 manuscripts/dpp-msbayes/dpp-msbayes.tex
Breaking up dpp ms into more files.
Moving abstract and acknowledgments to separate files, and also making
the title a macro.

\title{An Improved Approximate-Bayesian Model-choice Method for Estimating
Shared Evolutionary History}

@@

\begin{abstract}
    To understand the processes that generate biodiversity, it is
    important to account for large-scale processes that affect the evolutionary
    history of groups of co-distributed populations of organisms.
    Such events predict temporally clustered divergences times, a pattern
    that can be estimated using genetic data from co-distributed species.
    I introduce a new approximate-Bayesian model for comparative
    phylogeographical model-choice that estimates the temporal distribution of
    divergences across taxa from multi-locus DNA sequence data.
    The model is an extension of that implemented in \msb.
    By reparameterizing the model, introducing more flexible priors on
    demographic and divergence-time parameters, and implementing a
    non-parametric Dirichlet-process prior over divergence models, I improved
    the robustness, accuracy, and power of the method for estimating shared
    evolutionary history across taxa.
    The results demonstrate the improved performance of the new method is due
    to (1) more appropriate priors on divergence-time and demographic
    parameters that avoid prohibitively small marginal likelihoods for models
    with more divergence events,
    and (2) the Dirichlet-process providing a flexible prior on divergence
    histories that does not strongly disfavor models with intermediate numbers
    of divergence events.
    % The results demonstrate that the tendency of the \msb model to spuriously
    % support models of clustered divergences is caused by a combination of (1)
    % uniform priors on nuisance parameters hindering the marginal likelihoods of
    % models with more divergence-time parameters, and (2) a prior on divergence
    % models that disfavors models with intermediate numbers of divergence-time
    % parameters.
    The new method yields more robust estimates of posterior uncertainty, and
    thus greatly reduces the tendency of the model to incorrectly estimate
    biogeographically interesting models with strong support.

@@

\section{Acknowledgments}
I am greatful to Melissa Callahan, Mark Holder, Emily McTavish, Daniel Money,
Jordan Koch, and Adam Leach\'{e} for insightful comments that greatly improved
this work.
I thank the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
This work was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
I also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.

>>>>

\title{\dppTitle}

@@

\begin{abstract}
    \input{dpp-msbayes-abstract.tex}

@@

\section{Acknowledgments}
\input{dpp-msbayes-acknowledgments.tex}
